%========================================================================================
%
%   CONTENT.TEX - YOUR RESUME DATA
%   - All your personal information and resume text are defined here.
%   - This is the only file you need to edit for content updates.
%
%========================================================================================

%--- PERSONAL DETAILS (fill these in) ---
\renewcommand{\resumeName}{Anthony Tabano}
\renewcommand{\resumeLocation}{Hudson Valley, NY}
\renewcommand{\resumePhone}{845-849-4125}
\renewcommand{\resumeEmail}{anthony.tabano.dev@gmail.com}
\renewcommand{\resumeLinkedIn}{linkedin.com/in/anthonytabano}
\renewcommand{\resumeLocationUrl}{https://www.google.com/maps/place/Hudson+Valley}

%========================================================================================
%
%   RESUME BODY STARTS HERE
%   - This section uses the commands and settings defined in cv.tex
%
%========================================================================================
\pagestyle{empty} % No header/footer on any page

%----------------------------------------------------------------------------------------
%   HEADER
%----------------------------------------------------------------------------------------
{\fontsize{26pt}{30pt}\selectfont\bfseries\RaggedRight\color{colorHeadings}{\addfontfeature{LetterSpace=3.5}\resumeName}\par}
\vspace{\spacingAfterHeaderName}
{\small\noindent
\href{\resumeLocationUrl}{\textcolor{colorHeadings}{\faIcon{map-marker-alt}}\thinspace\resumeLocation}\contactSeparator
\href{tel:\resumePhone}{\textcolor{colorHeadings}{\faIcon{phone}}\thinspace\resumePhone}\contactSeparator
\href{mailto:\resumeEmail}{\textcolor{colorHeadings}{\faIcon{envelope}}\thinspace\resumeEmail}\contactSeparator
\href{https://\resumeLinkedIn}{\textcolor{colorHeadings}{\faIcon[brands]{linkedin}}\thinspace\resumeLinkedIn}
\par}
\vspace{\spacingAfterHeaderContact}

%----------------------------------------------------------------------------------------
%   SUMMARY
%----------------------------------------------------------------------------------------
\noindent \textbf{Senior Software Engineer} with 12+ years of experience translating complex requirements into mission-critical solutions. Expertise includes defining architectural roadmaps and delivering scalable solutions using Java, Spring Boot, and TypeScript in cloud-native environments. My background in Aerospace Engineering provides a rigorous, methodical approach to solving challenges in demanding, high-stakes environments.

\vspace{\spacingAfterSummary}

%----------------------------------------------------------------------------------------
%   TECHNICAL EXPERTISE
%----------------------------------------------------------------------------------------
\section*{Technical Expertise}
\renewcommand{\arraystretch}{1.4} % Increase row height in the table
\begin{tabularx}{\textwidth}{@{} >{\bfseries\scshape\raggedright}p{3.5cm} @{\hspace{1.0em}} X @{}}
    Backend & \small Java (11+), Spring Boot, Spring Framework (Core, Security, Batch), GraphQL, REST APIs, Apache Camel \\
    Frontend & \small TypeScript, Angular (11+), Next.js, Nx/Turborepo Monorepos, Single-SPA Micro-frontends, RxJS, NgRx, Storybook \\
    Data \& Messaging & \small PostgreSQL, SQL Server, MongoDB, Redis, Kafka, RabbitMQ, AWS SQS \\
    Cloud \& DevOps & \small Kubernetes (K8s), Docker, Helm, GitHub Actions, Azure DevOps (Pipelines), AWS, Azure, Datadog \\
    Additional & \small Python, NestJS, Node.js, Cypress, Playwright, JUnit, Mockito, Webpack \\
\end{tabularx}
\renewcommand{\arraystretch}{1} % Reset row height to default
\vspace{\spacingAfterSkills}

%----------------------------------------------------------------------------------------
%   PROFESSIONAL EXPERIENCE
%----------------------------------------------------------------------------------------
\section*{Professional Experience}

\jobtitle{Senior Software Engineer \& Manager}{buildit}{Remote}{Jan 2022 -- Present}
\clientrole{Client Engagement: Senior Software Engineer at Fortune 10 Healthcare}
\begin{itemize}[leftmargin=*, itemsep=\bulletItemSeparation, topsep=0pt]
    \item Pioneered the client's first Nx monorepo from concept to rollout, scaling to 150+ shared libraries and establishing a modern UI ecosystem that ensured a more stable and predictable release cycle.
    \item Introduced Single-SPA parcels to transform legacy frontend modules into on-demand, dynamically loaded components, an architectural shift that significantly improved key application performance metrics.
    \item Built high-performance Java APIs to power core business functions, including the enterprise rules and dynamic questionnaire engines, enabling new self-service capabilities for business users.
    \item Engineered production-grade CI/CD pipelines from scratch using GitHub Actions, Helm and Kubernetes, replacing a high-risk manual process and enabling consistent, zero-downtime releases.
    \item Managed a team of engineering managers and senior engineers, owning career development and reviews, while remaining fully billable as a hands-on Senior Engineer on the client engagement.
\end{itemize}
\vspace{\spacingBetweenJobs}

\jobtitle{Senior Software Engineer}{iptiQ by Swiss Re}{Armonk, NY (Hybrid)}{Aug 2020 -- Jan 2022}
\begin{itemize}[leftmargin=*, itemsep=\bulletItemSeparation, topsep=0pt]
    \item Led international team of 8 engineers to design and deliver core B2B2C life insurance sales SDKs (Spring Boot, Angular) enabling third-party platforms to seamlessly integrate and distribute life insurance products to their customers.
    \item Enhanced existing event-driven microservices platform using RabbitMQ and Kubernetes, significantly improving system resilience and uptime for high-traffic partnerships.
    \item Spearheaded multi-quarter modernization of 10+ legacy applications, upgrading Angular 8→12 and Spring Boot 2.1→2.5 to eliminate critical technical debt and resolve 50+ security vulnerabilities.
    \item Defined the engineering department's Git branching strategy and built and scaled automated CI/CD pipelines in Azure DevOps supporting 100+ engineers to establish standardized release processes across multiple product lines.
\end{itemize}
\vspace{\spacingBetweenJobs}

\jobtitle{Senior Software Engineer}{AutoNation}{White Plains, NY}{Jan 2019 -- Aug 2020}
\begin{itemize}[leftmargin=*, itemsep=\bulletItemSeparation, topsep=0pt]
    \item Replaced a legacy inventory ERP with a multithreaded Spring Batch application, reducing nightly data synchronization for 300+ dealerships from 5+ hours to under 15 minutes.
    \item Led end-to-end integration of a major third-party parts supplier, creating a critical e-commerce channel with new architecture, inventory sync and frontend product visualization.
    \item Built scalable RESTful microservices using Apache Camel, Spring Boot, Azure API Management, AWS, and SQS messaging to streamline labor and parts data retrieval, enhancing system responsiveness and delivering new taxonomy-driven features.
\end{itemize}
\vspace{\spacingBetweenJobs}

\jobtitle{Software Engineer \& Supervisor}{Teachers College, Columbia University}{New York, NY}{Dec 2016 -- Jan 2019}
\begin{itemize}[leftmargin=*, itemsep=\bulletItemSeparation, topsep=0pt]
    \item Built and deployed a financial automation tool integrated with the Banner ERP system, eliminating 40+ hours of manual data entry and reconciliation per month.
    \item Delivered a tuition benefits payment platform as sole engineer with Spring Boot and Angular; owning the full lifecycle from stakeholder discovery and architecture to university-wide rollout.
    \item Supervised a small team of data analysts and created a SQL training program, enabling self-service reporting and significantly reducing IT support requests.
\end{itemize}
\vspace{\spacingBetweenJobs}

\jobtitle{Aerospace \& Software Engineer (Multiple Roles)}{Sikorsky, a Lockheed Martin Company}{Stratford, CT}{Aug 2013 -- Dec 2016}
\begin{itemize}[leftmargin=*, itemsep=\bulletItemSeparation, topsep=0pt]
    \item \textbf{Software Engineer:} Transitioned from aerospace to software by [initially] self-learning C\#, Python and SQL to build data processing and automation tools, saving thousands of engineering hours annually.
    \item \textbf{Aerospace Engineer:} Analyzed flight computer telemetry and aircraft sensor data to predict component failures on critical systems with 1+ year lead times (e.g., gearboxes), preventing costly downtime by aligning supply chains with maintenance and design improvements for CH-53K and S-92 programs.
\end{itemize}
\vspace{\spacingBetweenJobs}

%----------------------------------------------------------------------------------------
%   EDUCATION
%----------------------------------------------------------------------------------------
\section*{Education}
\noindent
\begin{tabularx}{\textwidth}{@{}Xr@{}}
    \textbf{Master of Science, Computer Science} & \textbf{Sacred Heart University} \\
    \textbf{Bachelor of Science, Aerospace Engineering} & \textbf{Embry-Riddle Aeronautical University} \\
    \textbf{Bachelor of Science, Management} & \textbf{SUNY Morrisville} \\
\end{tabularx}
